Report on Certificate Tools

### 2016-08-27 TEX/draft.tex
Added text to git also changed back .tex file

\subsubsection{Viewing stored certificates}
\myparagraph{PEM encoded certificates (.pem$\vert$.cer$\vert$.crt):}

  \verb+openssl x509 -in sample_cert.extention -text -noout+

\myparagraph{DER encoded certificates (.der):}

  \verb+openssl x509 -in certificate.der -inform der -text -noout+

\myparagraph{Importing PEM or DER encoded keys or certificates into PKCS\#12 file:}

  \verb+openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem+

certfile option is used only if importing more certificates into a single PKCS\#12 file is wanted.

@@

@@

>>>>

\subsubsection{Viewing stored certificates}
\myparagraph{PEM encoded certificates (.pem$\vert$.cer$\vert$.crt):}
  \begin{verbatim}
  openssl x509 -in sample_cert.extention -text -noout
  \end{verbatim}
\myparagraph{DER encoded certificates (.der):}
  \begin{verbatim}
  openssl x509 -in certificate.der -inform der -text -noout
  \end{verbatim}
\myparagraph{Importing PEM or DER encoded keys or certificates into PKCS\#12 file:}
  \begin{verbatim}
  openssl pkcs12 -export -in file.pem -out file.p12 -name "My Certificate" -certfile othercerts.pem
  \end{verbatim}
certfile option is used only if importing more certificates into a single PKCS\#12 file is wanted.

@@

      \paragraph{Self-signed certificate}
      It is possible to generate private key and self signed certificate with 
      \begin{verbatim}
      openssl req -x509 -sha256 -nodes -days 365 -newkey rsa:2048 -keyout privateKey.key -out certificate_name.crt
      \end{verbatim}

      \paragraph{Certificate Signing Request}
      It is possible to generate private key and CSR with
      \begin{verbatim}
      openssl req -out CSR.csr -new -newkey rsa:2048 -nodes -keyout privateKey.key
      \end{verbatim}

@@

      \paragraph{Specify algorithm}
      Currently OpenSSL supports Public-key cryptography algorithms:
      RSA, DSA, Diffie-Hellman key exchange, Elliptic Curve

      In the past also support for GOST R 34.10-2001 but as of January 2016 deprecated (https://mta.openssl.org/pipermail/openssl-commits/2016-January/003023.html )
